Effects of COVID-19 related social media use on well-being

### 2023-07-11 index.Rmd
Major updates Implemented feedback

---
title: "The effects of COVID-19 related social media use on well-being"
---

On this website, you can find the companion material for the paper _The effects of COVID-19 related social media use on well-being_.

@@

- The paper, which you can read [in your browser](manuscript.html) or download as [pdf](manuscript.pdf). 
- The detailed code and summaries of the [analyses](analyses.html)
- [Additional analyses](analyses_additional.html).
- A list of the [items translated into English](items_english.html)
- A list of the [original items in German](items_german.html)
- The [preregistration](preregistration.html) 
- A list where I needed to [deviate](preregistration_changes.Rmd) from the preregistration.

>>>>

---
title: "Effects of COVID-19 related social media use on well-being"
---

On this website, you can find the companion material for the paper _Effects of COVID-19 related social media use on well-being_.

@@

- The paper, which you can read [in your browser](manuscript.html) or download as [pdf](manuscript.pdf). 
- The [set-up](analyses_setup.html) for the analyses, including session information, custom functions, data wrangling, and data imputation.
- The detailed code and summaries of the [analyses](analyses.html)
- [Additional analyses](analyses_additional.html).
- A list of the [items translated into English](items_english.html)
- A list of the [original items in German](items_german.html)
- The [preregistration](preregistration.html) 
- A list where I needed to [deviate](preregistration_changes.Rmd) from the preregistration.
